Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-01-20 src-latex/parts/10-introduction.tex
Typo in intro
Updates from Overleaf (#12)

Trade directories have been leveraged in a recent work to identify polluted urban soils \cite{bell2020automated} and locate all gas stations in the city of Providence over the last century.
In an ongoing research project we aim at producing structured spatio-temporal data from the entries in the Paris trade directories to study the transformations of the fraction of XIX\textsuperscript{th} century Parisian society reachable through these sources.
%Because they originate from several publishers, their content is organised following different indexing methods (by name, by activity or by address), is printed in various layouts, and uses different fonts.
Therefor, we investigate several state-of-the-art OCR and NER approaches to assess their usability to process the corpus.

>>>>

Trade directories have been leveraged in recent work to identify polluted urban soils \cite{bell2020automated} and locate all gas stations in the city of Providence over the last century.
In an ongoing research project, we aim at producing structured spatio-temporal data from the entries of the Paris trade directories to study the dynamics of the fraction of the the XIX\textsuperscript{th} century Parisian society reachable through these sources.
%Because they originate from several publishers, their content is organised following different indexing methods (by name, by activity or by address), is printed in various layouts, and uses different fonts.
Therefore, we investigate several state-of-the-art OCR and NER approaches to assess their usability to process the corpus.
